Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
minor fix.

\noindent Note that the placeholders library provide better keyword such as {\tt notImplemented} and {\tt todo}.
Next we wrote visible behaviors in Haddock annotation:

@@

Note that the authors are not fundamentalist.
If functions to be defined are simple enough,
we might implement them first withtout signatures.
And their signatures can be automatically
inserted by IDE (like ghc-mod) later
if Haskell compilers can infer correctly.
Also, we can cut and paste examples and their results
from Haskell interpreters to their Haddock annotations.

>>>>

\noindent Note that the placeholders library provide better keyword such as {\tt notImplemented} and {\tt todo}.
Next we write visible behaviors in Haddock annotation:

@@

Note that the authors are not fundamentalist.
If functions to be defined are simple enough,
we might implement them first withtout signatures.
And their signatures can be automatically
inserted by IDE (such as ghc-mod) later
if Haskell compilers can infer correctly.
Also, we can cut and paste examples and their results
from Haskell interpreters to their Haddock annotations.
